\documentclass{martell_cv}

\usepackage{lipsum}
\usepackage{enumitem}

\setname{Valerii}{Martell}
\setaddress{\ \ \ \ Kyiv/Ukraine}
\setmobile{+380931675757}
\setmail{valerii.martell@gmail.com}
\setposition{Software Engineer, Ph.D. student, Lecturer}
\setlinkedinaccount{https://www.linkedin.com/in/valerii-martell} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/valerii-martell} %you can play with color of the template (red is also nice..)
\setthemecolor{red} %you can play with color of the template (red is also nice..)


\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
\setcompanyname{Center for Project-Based Learning, D-ITET,  ETH Zurich}
\setcontactperson{Sir or Madam}
\setclaimedposition{Junior Software Engineer} 
\coverletter{
\indent \par
I am writing to apply for the position of Junior Software Engineer as advertised on the ETHZ Job Board website. I believe that I am well suited for this position for a number of reasons.\par
During my studies and work at the university, I developed a vision of a deep problem in the education system - the lack of students' real experience, close to what they will face in their professional practice. I was going to build the teaching aspect of my career on the basis of the most practical training, where students after graduation would have at least one project, which is not ashamed to indicate in their resumes. The activities of your center, which I read about on your website, correlate as much as possible with my thoughts, we have the same views on the future of engineering education.\par
I am building my career at the intersection of academia and industry. I have experience in both scientific development and conducting experiments, and applied development. I have experience in managing small teams and in teaching, both individually and in groups. I also have a broad knowledge base in Computer Science and development with the use of different programming languages, hence the opportunities: 
\begin{itemize}[topsep=2pt,itemsep=2pt,partopsep=2pt, parsep=2pt]
  \item to join the development process in a short time, and, if necessary, quickly mastering a new programming language and its accompanying technology stack required for a particular project;
  \item to prepare practical courses and consultations for students in the necessary programming languages and/or other aspects of Computer Science.
\end{itemize}\par
Among my soft skills, I can highlight good communication skills, and experience in communicating with people of different professions (professors, scientists, programmers, managers, etc.). Сorrectness, politeness, professionalism, and courtesy are the cornerstones of my communication. I know how to avoid and smooth out conflict situations through open dialogue and finding compromises. At the same time, I am very hardworking, attentive to details, always try to think things through, and can work overtime in critical situations. I have a good memory, imagination, and excellent analytical skills.\par
I am currently a Ph.D. student, but due to the war, I can now postpone my Ph.D. to focus entirely on work. I can offer all the above-mentioned professional and personal qualities to the PBL team, and guarantee that I will do my best to become an important member of the team and push forward development and teaching excellence at ETHZ. 

My CV and a list of specific project proposals are enclosed for your convenience. Feel free to contact me at phone number or e-mail address mentioned above. I look forward to hearing from you. Thank you for your time and consideration.
\par \ \ \par
Yours faithfully,\par 
Valerii Martell.\par \ \ \par \ \ 
\par P.S. Just before the war, I legally changed my last name due to family circumstances (supporting documents: \href{https://drive.google.com/drive/folders/1OXNxW5fuXCGw8zo44h5djY0wQFQ2tmv9?usp=sharing}{[1]}). All official documents have already been updated, just did not have time to update certificates and diplomas before the war, there you can see my old last name - Demchyk. I am going to immediately update them after the war.
}
%Footnote
\createfootnote
\end{document}